\section{Data}
The following will include a thorough description and visualisation of the data acquired for the research, and how it was processed.

\subsection{\ac{ehm} Data}
The majority of data used for the research is \ac{ehm} data. This data was recorded by sensors in 231 BR725 engines during a total of \numprint{14045} flights, and returned on a voluntary basis to Rolls-Royce by customers. Each aircraft using the BR725 has two engines; to minimise the amount of data used, the values used in this thesis were taken from the left engine only.

\subsection{Parameters of Interest}
Each flight is represented by a CSV file with 216 columns, comprising one timestamp and 215 values per second of recording time.

The four flight parameters extracted were altitude (ALT), rotational speed of the high-pressure shaft (NH), and pressure and temperature of air exiting the compressor (P30 and T30, respectively).

\subsection{Flight Phases}
Each flight can be split into several phases: preflight, taxi out, take-off, climb, cruise, descent, reverse thrust and taxi in.

\subsection{Description}
The flights range in length from \numprint{1013} to \numprint{57062} seconds (approximately 0.28 to 15.85 hours), with a mean length of 10182.82 seconds and a standard deviation of 9561.03 seconds. A histogram of all flights is shown in Figure \ref{fig:flt_len}.

\subsection{Output}
The flights were processed using SA66 (Section \ref{sa66}) to determine the number of cycles consumed

\subsubsection{Cycle Counter}

\subsection{Visualisation}

\subsection{Downsampling}

\subsubsection{(A)PLA}

\subsubsection{APCA}

\subsection{Case Studies}

\subsubsection{6014: Stress Ranges}

\subsubsection{6079: Long Taxi}